Risk Perceptions for Wearable Devices

### 2015-03-03 tex-inputs/appendix/riskbenefit-table.tex
get rid of redundant files and confusing folders
added images for risk benefit table again

location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\

Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\

Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk}  & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\

\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

>>>>

location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialrecognitionben} \\

Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/LawnmowerRisk} & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/ElectricityBenefit} \\

Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/MotorcycleRisk}  & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/MotorcycleBenefit} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/HandgunRisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/HandgunBenefit} \\

\hline
\end{tabular}
\caption{Risks and benefit for all technologies.}
\label{allriskben}
\end{center}
\end{table}
